---
title: "Segmentation"
author: "Daniel"
date: "13/09/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Setup 

```{r import, message=FALSE, warning=FALSE}
library(janitor)
library(cluster)
library(tidyverse)
library(readxl)
library(summarytools)
library(Rtsne)
library(skimr)
library(forcats)
library(rmarkdown)
# render("C:/Users/u5800723/clustering_analysis/report.Rmd")
```


# Read in the raw data 

```{r read, message=FALSE, warning=FALSE}
cohort_res_raw <- read_csv("data/cohort_res_raw.csv") %>%
  clean_names()
```

# Data Cleaning and Processing 

```{r clean}
# Take and clean features of interest
cohort_cleaned <- cohort_res_raw %>%
  select(
    uid,
    gpa_course_count,
    age_group,
    gender,
    is_indigenous_flag,
    is_disabled_flag,
    disability_advice,
    first_in_family,
    catering_type,
    owner,
    religious_affiliation,
    weekly_tariff_grouping,
    program_career,
    field_of_education_broad_description,
    program_type,
    program_plan_group,
    appointment_flag,
    home_state,
    home_australia_ses,
    home_low_ses,
    home_metropolitan,
    home_regional,
    home_remote,
    basis_of_admission,
    attendance_type,
    citizenship,
    entrance_score_group_5,
    drive_time_band2,
    v_permit_no_days,
    cello_parked_flag,
    cello_parking_days,
    academic_skills_booked,
    academic_skills_dropin
  ) %>%
  replace_na(
    list(
      home_metropolitan = 0,
      home_regional = 0,
      home_remote = 0,
      cello_parking_days = 0,
      academic_skills_booked = 0,
      academic_skills_dropin = 0,
      v_permit_no_days = 0,
      hall_residence = "Off campus",
      catering_type = "off campus",
      owner = "off campus",
      religious_affiliation = "unknown",
      weekly_tariff_grouping = "off campus",
      field_of_education_broad_description = "09 - Society and Culture"
    )
  ) %>%
  mutate(
    home_overseas = ifelse(home_state == "Overseas", 1, 0),
    is_local = ifelse(home_state == "ACT", 1, 0),
    is_minority = ifelse(
        home_australia_ses == "Low" |
        basis_of_admission == "Mature age special entry" |
        is_indigenous_flag == 1 |
        is_disabled_flag == 1 |
        first_in_family == 1,
      yes = 1,
      no = 0
    ),
    field_of_education_broad_description = ifelse(
      field_of_education_broad_description == "00 - Not Allocated",
      yes = "03 - Engineering and Related Technologies",
      no = field_of_education_broad_description
    ),
    program_plan_group = fct_recode(
      program_plan_group, 
      double = "Flexible Doubles", 
      double = "Vertical Double"),
    religious_affiliation = fct_recode(
      religious_affiliation,
      religious = "Anglican",
      religious = "Christian"
    ),
    age_group = ifelse(age_group == "< 17 Years", "17 below Years", age_group),
    age_group = ifelse(age_group == "> 59 Years", "59 above Years", age_group)
  ) %>%
  mutate_at(
    c(
      "cello_parked_flag",
      "disability_advice",
      "first_in_family",
      "home_low_ses",
      "is_disabled_flag",
      "is_indigenous_flag",
      "appointment_flag",
      "is_local",
      "is_minority"
    ),
    as.factor
  ) %>%
  mutate_if(is.character, as.factor) %>%
  mutate(age_group = factor(age_group, ordered = TRUE),
         drive_time_band2 = factor(drive_time_band2, ordered = TRUE),
         entrance_score_group_5 = factor(entrance_score_group_5, ordered = TRUE),
         home_australia_ses = factor(home_australia_ses, ordered = FALSE),
         uid = as.character(uid),
         entrance_score_group_5 = fct_collapse(
           entrance_score_group_5,
           "64 below" = c("30 - 34", "35 - 39", "40 - 44", "45 - 49", "50 - 54", "55 - 59", "60 - 64"))
         ) %>%
  mutate(
    age_group2 = fct_collapse(
      age_group,
      "24 below Years" = c(
        "17 below Years",
        "17 Years",
        "18 Years",
        "19 Years",
        "20 Years",
        "21 Years",
        "22 Years",
        "23 Years",
        "24 Years"
      ),
      "25 - 29 Years" = c("25 Years", "26 Years", "27 Years", "28 Years", "29 Years"),
      "50 above Years" = c("50 - 59 Years", "59 above Years")
    )
  ) %>% 
  mutate(age_group2 = factor(
    age_group2,
    ordered = TRUE,
    levels = c(
      "24 below Years",
      "25 - 29 Years",
      "30 - 39 Years",
      "40 - 49 Years",
      "50 above Years"
    )
  )) %>%
  filter(!is.na(home_state))

```

## Cluster Preparation  

### Select a subset of variables  

```{r subset}
cohort_subset <- cohort_cleaned %>% 
  select(program_career, is_minority, appointment_flag, is_local) 
```


### Calculate Distance Matrix  

```{r dist}
diss_matrix <- daisy(cohort_subset, metric = "gower")
```


## Run Clustering Method  


### Optimise Validation Method  

```{r sil}
search_gird <- 2:4

search <- tibble(cluster = search_gird) %>% 
  mutate(ave_sw = map_dbl(.x = cluster, 
                          .f = ~pam(x = diss_matrix, 
                                    k = .x, 
                                    diss = TRUE)$silinfo$avg.width))

# graph output of silhouette coefficient
ggplot(search, aes(cluster, ave_sw)) +
  geom_line() +
  labs(title = "Which value of k returns the best silhouette coefficient",
       subtitle = "Using a heuristic we can pick the Min value of k that gives a reasonable result",
       y = "Average Silhouette Coefficient",
       x = "Number of clusters (k)")
```


### Run final method

```{r pam, message=FALSE, warning=FALSE, include=FALSE}
pam_fit <- pam(diss_matrix, k = 3, diss = TRUE)
summary(pam_fit)
```


## Interpretation  

### Attach Labels  

```{r re-attach}
# attaching cluster labels
clustered_cohort <- cohort_cleaned %>% 
  mutate(cluster = pam_fit$clustering)

```

### T-SNE Plot

```{r tsne}
# Embed clusters in 2D for visualisation
tsne_obj <- Rtsne(X = diss_matrix, is_distance = TRUE)

# extract projected data points, add cluster assingment and make data frame
tsne_data <- tsne_obj$Y %>%
  data.frame() %>%
  setNames(c("X", "Y")) %>%
  mutate(cluster = factor(clustered_cohort$cluster),
         label = clustered_cohort$program_career) 

# create mean of each cluster to add as centroid
tsne_summ <- tsne_data %>% 
  group_by(cluster) %>% 
  summarise(X = mean(X), 
            Y = mean(Y))

# create convex hulls 
hulls <- tsne_data %>% 
  group_by(cluster) %>% 
  slice(chull(X, Y))

# plot the clusters and nets
tsne_data %>% 
ggplot(aes(x = X, y = Y)) +
  geom_point(aes(color = cluster), show.legend = FALSE) +
  geom_text(data = tsne_summ, aes(X, Y, label = cluster), size = 7) +
#  geom_text(aes(X, Y, label = label), check_overlap = TRUE) +
  geom_polygon(data = hulls, aes(X, Y, fill = cluster), alpha = 0.7, show.legend = FALSE) +
  theme_minimal() +
  labs(title = "Cluster results of cohor data",
       subtitle = "picking n clusters") +
  theme(panel.grid = element_blank(), 
        axis.text = element_blank(), 
        axis.title = element_blank())
```


### Summary Statistics  

```{r summary, eval=FALSE}
clustered_cohort %>%  
  group_by(cluster) %>% 
  dfSummary(plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE)
```

### Extract the prototypes  

```{r centers}
prototypes <- clustered_cohort[pam_fit$medoids,]
```


## Write Results

```{r write}
write_csv(clustered_cohort, 'data/clustered_cohort.csv')
write_csv(prototypes, 'data/proto.csv')
```



# Appendix  

## Compare new records  

```{r new records, eval=FALSE}
# lets sample a 'new' student 
n <- 2

sample <- cohort_cleaned[sample(n),] %>% mutate(cluster = seq(n) +99)

compare <- bind_rows(sample, prototypes) %>% 
  column_to_rownames(var = "cluster") %>% 
    select(program_career, is_minority, appointment_flag, is_local) 

dm <- daisy(compare, metric = "gower")

dm_mat <- as.matrix(dm)

x <- dm_mat[seq(n), -seq(n)]

apply(x, MARGIN = 1, FUN = function(x) which(x == min(x)))

```



## Multiple Comparisons  

* ANOVA  
* lm  


```{r stat test}



```






















